### 2020-02-10 report.tex
some edits

Our alternative method is "trail saving", where we cache the part of the trail that is unassigned during a backtrack and then attempt to restore implied parts of it as each new decision is made. Trail saving preserves the traditional invariants of the SAT solver and its basic version is very simple to implement. It also allows the search to choose the order of decisions, but helps make propagation faster. We explore the theoretical speedup that trail saving provides, develop some enhancements to make the idea more effective, and demonstrate experimentally that it speeds up state-of-the-art SAT solvers by a non-trivial factor.

>>>>

Our alternative method is "trail saving", where we cache the part of the trail that is unassigned during a backtrack and then attempt to restore implied parts of it as each new decision is made. Trail saving preserves the traditional invariants of the SAT solver and its basic version is very simple to implement. It also allows the search to choose the order of decisions, but helps make propagation faster. We explore the theoretical speedup that trail saving provides, develop some enhancements to make the idea more effective, and demonstrate experimentally that it performs similarly well as chronological backtracking without suffering from some of the aforementioned drawbacks.
